Mental Health Factors and Covid

### 2025-04-20 products/manuscript/Manuscript.qmd
Part 5 manuscript updates

Binary variables were created to allow for interpretability. EXERCISE is a combination of number of minutes of passive or aerboic exercise, descirbing whther weekly amount meets the American Heart Association's guidelines for exercise needed to stay healthy, as exercise is known to relate to mental health. SLEEP is based on the NIH guidelines for recommended hours of sleep per day, which differs by age.

Complex survey design was used to allow for generalizability of results, using vairbales PSU, STRATA, and SAMPWEIGHT.

>>>>

Binary variables were created to allow for interpretability. EXERCISE is a combination of number of minutes of passive or aerboic exercise, descirbing whther weekly amount meets the American Heart Association's guidelines for exercise needed to stay healthy, as exercise is known to relate to mental health. SLEEP is based on the NIH guidelines for recommended hours of sleep per day, which differs by age. DEPRESSED includes if the individual reports feeling depressed on a weekly or daily basis, but not at a frequency of monthly or less. TROUBLE_SLEEPING indicates struggling to fall asleep several days per week, more than half the days, or nearly every day. SOCIAL describes individual feeling like they have less social support than their regular amount. Answers for don't know or unsure were converted to missing.

After creating binary variables, significant amounts of data were missing. Multiple imputation was used to create 5 sets of imputed data, and used for the remainder of analysis. To calculate later statisitcs, processes were preformed on each of the 5 sets and then averaged.

Complex survey design was used to allow for generalizability of results, using variables PSU, STRATA, and SAMPWEIGHT. A summary table was generated to find occurence of each of the factors and their inverses among the data. Next, single models were ran to find associations between each variable with covid test postivity. To explore the data further, a multivariate model, LASSO regression, and a third advanced model (replace this) were ran with cross validation.
